Self Regulation Ontology Retest Analyses

### 2018-07-26 code/SRO_Retest_Analyses.Rmd
updating stats

# summary(lm(icc ~ num_all_trials, data = tmp))
# summary(lmerTest::lmer(icc ~ num_all_trials + (1|dv), data = tmp))
summary(MCMCglmm(icc ~ num_all_trials, random=~dv, data = tmp))
```

>>>>

# summary(lm(icc ~ num_all_trials, data = tmp))
# summary(lmerTest::lmer(icc ~ num_all_trials + (1|dv), data = tmp))
m = readRDS('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/icc_by_num_trials_model.rds')
summary(m)
```
